---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bunchcomputing

<!-- badges: start -->
<!-- badges: end -->

The goal of bunchcomputing is to compute summary statistics(means,median) on every columns in the dataframe.

## Installation

bunchcomputing is not yet on CRAN. But, you can download it from this repository using the following R command:

``` r
devtools::install_github("WYC401/WYC_function")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bunchcomputing)
mean_all_numeric_variables(data.frame(data_1=c(1,2,3),data_2=c(0.2,0.4,0.4)))

## basic example code
```

The package is special because it can ignore the non-numeric columns.
```{r}
library(bunchcomputing)
mean_all_numeric_variables(base::data.frame(a=c(1,2),b=c("d","d")))
```
